---
title: "MATH216 HW 1"
author: "MJ Pascual"
date: "September 20, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# set up environment, declare variables, read data
library(ggplot2)
library(tidyverse)

plants <- read.csv(file = "Plants.csv")
## plants <- filter(plants, Row > 1)
plants$Species <- factor(plants$Species)
plants$Fert <- factor(plants$Fert)
```


## Question 1
```{r}
table(plants$Species, plants$Fert)
```

Based on the table, the experimental design is reasonable becase there is an almost equal amount of the each fertilizer with each species.

## Question 2

```{r}
ggplot(data = plants, mapping = aes(x = Species, y = BiomassT2)) + 
  geom_boxplot()
```

While the medians are similar, species 1 has a smaller variation than species 2 and 3. Species 3 has the smallest biomass while species 2 has the largest biomass. 


## Question 3

```{r}
plant1 <- subset(plants, Species == "1")
plant2<- subset(plants, Species == "2")
plant3 <- subset(plants, Species == "3")

mean(plant1$BiomassT2)
mean(plant2$BiomassT2)
mean(plant3$BiomassT2)
```

## Question 4

```{r}
ggplot(data = plants, mapping = aes(x = Fert, y = BiomassT2)) + 
  geom_boxplot()
```

The graph is showing that there is a significant difference between the type of fertilizer used and the final biomass. In rising order of final biomass, it goes from C to B to A. B has more variation in comparison to A and B. A and C does have some outliers, but none important enough.

## Question 5
```{r}
ggplot(data = plants, mapping = aes(x = Species , y = BiomassT2)) + 
  geom_boxplot(aes(fill = Fert))
```

Regardless of the species, the order of fertilizer remained the same for all 3 spexxies. However, the variations were different between the different species. 

## Question 6

```{r}
ggplot(data = plants, mapping = aes(x = BiomassT1, y = BiomassT2)) + 
  geom_point()
```

There is a linear relationship between the starting biomass and the final biomass. If the starting biomass (BiomassT1) is high, then the final biomass will also be high and vice versa for low. 

## Question 7

```{r}
ggplot(data = plants, mapping = aes(x = BiomassT1, y = BiomassT2)) + 
  geom_point(aes(color = Fert, size = Species))
```

The linear relationship is caused by a specic order. The order of growth is by fertilizer where C caused the lowest growth, then B, and A resulted in the highest growth. There are outliers under Biomass 80 and so I'd take out row 1.

## Question 8

```{r}
ggplot(data = plants, mapping = aes(x = Row, y = Column)) +
  geom_point(aes(size = BiomassT2))
```


## Question 9

```{r}
ggplot(data = plants, mapping = aes(x = Row, y = Column)) +
  geom_tile(aes(fill = BiomassT2))
```

## Question 10 
```{r}

```

Solution: remove row 1 because it's causing most of the outliers. 

## Question 11
```{r}
biomassT1.avg <- mean(plants$BiomassT1)
biomassT2.avg <- mean(plants$BiomassT2)

```
