---
title: "MATH216 HW 1"
author: "MJ Pascual"
date: "September 20, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# set up environment, declare variables, read data
library(ggplot2)

plants <- read.csv(file = "Plants.csv")
plants$Species <- factor(plants$Species)
plants$Fert <- factor(plants$Fert)
```


## Question 1
```{r}
table(plants$Species, plants$Fert)
```

Based on the table, the experimental design is reasonable becase there is an almost equal amount of the each fertilizer with each species

## Question 2

```{r}
ggplot(data = plants, mapping = aes(x = Species, y = BiomassT2)) + 
  geom_boxplot()
```

While the medians are similar, species 1 has a smaller variation than species 2 and 3. Species 3 has the smallest biomass while species 2 has the largest biomass. 


## Question 3: GET HELP

```{r}
biomass.plant1 <- subset(plants, Species == "1")
biomass.plant2<- subset(plants, Species == "2")
biomass.plant3 <- subset(plants, Species == "3")

mean(biomass.plant1)
mean(biomass.plant2)
mean(biomass.plant3)
```

## Question 4

```{r}
ggplot(data = plants, mapping = aes(x = Fert, y = BiomassT2)) + 
  geom_boxplot()
```

The graph is showing that there is a significant difference between the type of fertilizer used and the final biomass.