---
title: "Mini-Lab"
author: "Josh Yuan, Tina Chen, MJ Pascual, & Fiona Mohammed"
date: "October 20, 2017"
output: html_document
---
```{r}
## Set up packages
library(tidyverse)
library(tidyr)
library(dplyr)
library(ggplot2)

```

## Skittles

One-Proportion Test

Claim: Skittles colors are represented equally

1. Assumptions: Random sample
                np >= 10 and n(1-p) >= 10
                102(0.20) > 10, 102(1-0.20) >= 10
                20.4 > 10, 81.6 >= 10
                
2. Hypotheses: Ho: p  = 0.20
               Ha: p != 0.20
               
```{r}
#Purple
binom.test(18, 102, 0.20)

#Green
binom.test(20, 102, 0.20)

#Red
binom.test(19, 102, 0.20)

#Yellow
binom.test(20, 102, 0.20)

#Orange
binom.test(25, 102, 0.20)
```

               
3. Test statistic: Binomial Test
                   centered at 0.20
                  
                  Purple
                  number of successes = 18
                   
                  Green
                  number of successes = 20
                   
                  Red
                  number of successes = 19
                   
                  Yellow
                  number of successes = 20
                   
                  Orange
                  number of successes = 25
                  
                  
 4. p-values:
                  Purple
                  p-value = 0.6216
                   
                  Green
                  p-value = 1
                   
                  Red
                  p-value = 0.8052
                   
                  Yellow
                  p-value = 1
                   
                  Orange
                  p-value = 0.2649


5. Benjamin-Hochberg (BH) Correction:

                  Purple
                  p-value = 1
                   
                  Green
                  p-value = 1
                   
                  Red
                  p-value = 1
                   
                  Yellow
                  p-value = 1
                   
                  Orange
                  p-value = 1


```{r}
p.values <- c(0.6216, 1, 0.8052, 1, 0.2649)
p.adjust(p.values, method = "BH")
```


 6. Conclusion
   For each color of skittles, there is virtually a 100% chance that the difference from the null hypothesis (that 20% of our sample would be orange) was due to chance alone. There is therefore no evidence to reject the null hypothesis that each color of Skittles is represented equally.


```{r}
skittles <- data.frame(skittle.color = c("Purple", "Green", "Red", "Yellow", "Orange"),
    count = c(18, 20, 19, 20, 25))

#Bar Plot
ggplot(skittles, aes(skittle.color, count)) + geom_col()
skittle.bar<- ggplot(skittles, aes(x="", y=count, fill=skittle.color)) +
  geom_bar(width = 1, stat = "identity") + xlab("Color") + ylab("Count")

skittle.bar

#Pie Chart
skittle.pie <- skittle.bar + coord_polar("y", start=0)
skittle.pie + scale_fill_manual(values=c("green", "orange", "purple", "red", "yellow"))
```

## M&M's

Claim: M&Ms colors are represented equally

1. Assumptions: Random sample
                np >= 10 and n(1-p) >= 10
                138(0.1667) > 10, 138(1-0.1667) >= 10
                
                23 > 10, 114.99 >= 10

2. Hypotheses: 
        Ho: p  = .1667
        Ha: p != .1667

3. Test statistic: 
        Binomial Test
        centered at: 
            looks somewhat close to normal

```{r}
prop_m <- c(20,22,26,26,16,28)
pv <- c(0.5683,0.9092,0.493,0.493,1,0.003238)
orange <- binom.test(20,138,.1667) #not equal to p
green <- binom.test(22,138,.1667) #not equal to p
blue <- binom.test(26,138,.1667) #not equal to p
yellow <- binom.test(26,138,.1667) #not equal to p
brown <- binom.test(16,138,.1167) #not equal to p
red <- binom.test(28,138,.1167) #not equal to p
```

From our test sample, we may conclude that the true probability success is not equal to the null hypothesis. 

``` {r}
new_name<- c("Orange","Green","Blue","Yellow","Brown","Red")

new_prop_m <- prop_m %>% 
  as.data.frame()

new_name <- new_name %>% 
  as.data.frame()

pv <- pv %>% 
  as.data.frame()

data <- cbind(new_name,pv)

ggplot(data = data, aes(x = new_name, y =.)) +
  geom_bar(stat = "identity") +
  xlab("M&M colors") +
  ylab("Number of M&Ms")

p.adjust(data$.,method="BH")
[1] 0.852450 1.000000 0.852450 0.852450 1.000000 0.019428

```


